Global patterns of forest autotrophic carbon fluxes

### 2020-06-05 manuscript/manuscript draft.Rmd
(slow) progress on HML comments
I've incorporated (or opened issues for) all comments prior to analyses section of Methods.

#81

ForC contains geographic coordinates associated with each measurement record and, when available, mean annual temperature (MAT) and mean annual precipitation (MAP) as reported in the primary literature [@anderson-teixeira_forc_2018]. Based on the geographic co-ordinates for each site, data on twelve climate variables--including MAT, MAP, temperature and precipitation seasonality, annual temperature range, solar radiation, cloud cover, annual frost and wet days, potential evapotranspiration (PET), aridity (MAP/PET), and vapor pressure deficit (VPD)--were extracted from five open-access climate datasets: WorldClim [@hijmans_very_2005], WorldClim2 [@fick_worldclim_2017], the Climate Research Unit (CRU) time-series dataset v. 4.03 [@harris_updated_2014], the Global Aridity Index and Potential Evapotranspiration Climate Database [@trabucco_global_2019], and TerraClimate [@abatzoglou_terraclimate_2018] (Table S1). From these data, we derived maximum VPD, defined as the VPD of the month with the largest deficit, and the number of water stress months, defined as the number of months annually where precipitation was lower than PET. Where site-level data was missing for MAT or MAP, we used values from the WorldClim dataset.

Length of the growing season was estimated to the nearest month, where growing season months were defined as months with mean minimum temperature > 0.5$^\circ$C. We experimented with a definion of growing season months including a moisture index, defined as (MAT - PET)/PET, > -0.95 [@kerkhoff_plant_2005; see also @michaletz_convergence_2014]. However, we found that including a moisture index had **no** effect on the estimates of growing season length, and so chose to exclude it.  (**Becky, was it really no effect? or minimal?**) Monthly data for PET, precipitation, and temperature from the CRU dataset v 4.03 [@harris_updated_2014], and solar radiation from WorldClim2 [@fick_worldclim_2017] were used to calculate mean monthly PET, precipitation, temperature and solar radiation during the growing season. Total growing season precipitation and solar radiation were also calculated.

>>>>

ForC contains geographic coordinates associated with each measurement record and, when available, mean annual temperature (MAT) and mean annual precipitation (MAP) as reported in the primary literature [@anderson-teixeira_forc_2018]. Based on the geographic co-ordinates for each site, data on twelve climate variables--including MAT, MAP, temperature and precipitation seasonality, annual temperature range, solar radiation, cloud cover, annual frost and wet days, potential evapotranspiration (PET), aridity (MAP/PET), and vapor pressure deficit (VPD)--were extracted from five open-access climate datasets: WorldClim [@hijmans_very_2005], WorldClim2 [@fick_worldclim_2017], the Climate Research Unit time-series dataset (CRU TS v4.03 [@harris_updated_2014], the Global Aridity Index and Potential Evapotranspiration Climate Database [@trabucco_global_2019], and TerraClimate [@abatzoglou_terraclimate_2018] (Table S1). From these data, we derived maximum VPD, defined as the VPD of the month with the largest deficit, and the number of water stress months, defined as the number of months annually where precipitation was lower than PET. Where site-level data was missing for MAT or MAP, we used values from the WorldClim (**[2?](https://github.com/forc-db/Global_Productivity/issues/89)**) dataset.

Length of the growing season was estimated to the nearest month, where growing season months were defined as months with mean minimum temperature > 0.5$^\circ$C. We experimented with a definion of growing season months including a moisture index, defined as (MAT - PET)/PET, > -0.95 [@kerkhoff_plant_2005; see also @michaletz_convergence_2014]. However, we found that including a moisture index had minimal effect on the estimates of growing season length, and so chose to exclude it. Monthly data for PET, precipitation, and temperature from the CRU dataset v 4.03 [@harris_updated_2014], and solar radiation from WorldClim2 [@fick_worldclim_2017] were used to calculate mean monthly PET, precipitation, temperature and solar radiation during the growing season. Total growing season precipitation and solar radiation were also calculated.
